### 2014-07-28 paper/paper.tex
Fixed the second reader's name. Hopefully.
Wrote much of the introduction. It's not the best but it could be much worse

Professor Lee % TODO which professor Lee?

@@

\subsection{Topic Area}
\subsection{Specific Problem}
\subsection{Task Description}

>>>>

Professor Xining Li

@@

A great deal of modern communications technologies allow people to discuss and
disseminate their opinions with a near negligible cost. Since the extremely low
cost allows everyone to share their opinions, the scale of textual data is
enormous. In order to gain insight into the `overall' opinion on particular
topics, the process of determining sentiment must be automated.

\subsection{Topic Area}

Sentiment analysis is simply a classification task that attempts to label
fragments of text with a label that appropriately summarizes the attitude of
the text. Natural Language Processing (NLP) provides a number of method for
preforming sentiment analysis. Many of these methods take a probabilistic
approach to performing the task.

%TODO how could this be useful

\subsection{Specific Problem}

The focus of this undergraduate research project has been to preform sentiment
analysis in data from the microbloging website Twitter. This data presents some
interesting problems to performing good sentiment analysis due to it's short
and informal nature. All of the messages, known as Tweets, are constrained in
length to 140 characters. This limit forces many users of Twitter to use
abbreviations and contractions. Twitter makes it extremely easy to publish a
Tweet and has no way to edit a Tweet once published. This results more spelling
and grammar mistakes then other sources of text. Tweets often also contain
links to other websites in the form of URLs as well as taging system for topics
and other users.

\subsection{Task Description}

Organizers of the SemEval-2013 workshop created various sentiment analysis
tasks to be preformed. The task focused on for this project was task-2b:
Message polarity classification. The organizers used the amazon service
``Mechanical Turk" to get many humans to annotate Tweets as `positive',
`negative' or `neutral'. In tweets with mixed sentiments the prevailing
sentiment was chosen. Participants were tasked with creating a classifier to
establish labels for Tweets not in the training dataset. The various
submissions of the participants were then evaluated by the average of the
F-positive and the F-negative.
